# Results

This chapter presents the findings from the data analysis, organized by research question and hypothesis. The results are presented objectively without interpretation, which will be addressed in the Discussion chapter.

## Data Collection Summary

### Response Rate

- **Total participants contacted**: N = [number]
- **Completed responses**: N = [number]
- **Response rate**: [percentage]%
- **Excluded responses**: N = [number] (reasons: [list reasons])
- **Final sample size**: N = [number]

### Data Quality

- **Missing data**: [percentage]% overall
- **Complete cases**: N = [number]
- **Data cleaning procedures**: [brief summary of procedures applied]

## Descriptive Statistics

### Participant Characteristics

#### Demographic Information

```{r}
#| label: tbl-demographics
#| tbl-cap: "Participant Demographics"

# Demographic table will be generated here
```

**Table 4.1** presents the demographic characteristics of the sample:

- **Age**: M = [mean], SD = [standard deviation], Range = [range]
- **Gender**: [breakdown by categories]
- **Education level**: [breakdown by categories]
- **Other relevant demographics**: [additional characteristics]

### Variable Distributions

#### Primary Variables

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive Statistics for Primary Variables"

# Descriptive statistics table will be generated here
```

**Table 4.2** shows descriptive statistics for all primary variables:

- **Variable 1**: M = [mean], SD = [standard deviation], Skewness = [value], Kurtosis = [value]
- **Variable 2**: M = [mean], SD = [standard deviation], Skewness = [value], Kurtosis = [value]
- **Variable 3**: M = [mean], SD = [standard deviation], Skewness = [value], Kurtosis = [value]

#### Distribution Assessment

```{r}
#| label: fig-distributions
#| fig-cap: "Distribution of Primary Variables"

# Histogram/density plots will be generated here
```

**Figure 4.1** displays the distributions of primary variables. [Brief description of distribution patterns and any notable features].

## Assumption Testing

### Statistical Assumptions

#### Normality

- **Shapiro-Wilk tests**: [Results summary]
- **Q-Q plots**: [Visual assessment results]
- **Kolmogorov-Smirnov tests**: [Results if applicable]

#### Linearity

```{r}
#| label: fig-linearity
#| fig-cap: "Scatterplot Matrix for Linearity Assessment"

# Scatterplot matrix will be generated here
```

**Figure 4.2** shows scatterplots examining linearity assumptions. [Brief description of linearity assessment].

#### Homoscedasticity

- **Levene's test**: F([df1, df2]) = [value], p = [p-value]
- **Breusch-Pagan test**: χ²([df]) = [value], p = [p-value]

#### Multicollinearity

```{r}
#| label: tbl-correlation
#| tbl-cap: "Correlation Matrix and Multicollinearity Statistics"

# Correlation matrix with VIF values will be generated here
```

**Table 4.3** presents the correlation matrix and variance inflation factors (VIF). All VIF values were below [threshold], indicating no multicollinearity concerns.

## Research Question 1: [Question Text]

### Hypothesis 1: [Hypothesis Statement]

#### Primary Analysis

```{r}
#| label: tbl-rq1-primary
#| tbl-cap: "Primary Analysis Results for Research Question 1"

# Analysis results table will be generated here
```

**Primary Statistical Test**: [Test name]
- **Test statistic**: [statistic] = [value]
- **Degrees of freedom**: [df]
- **p-value**: p = [value]
- **Effect size**: [effect size measure] = [value]
- **Confidence interval**: [CI range]

**Result**: [Brief statement of statistical significance and direction]

#### Secondary Analysis

```{r}
#| label: fig-rq1-visualization
#| fig-cap: "Visualization of Results for Research Question 1"

# Relevant plot/graph will be generated here
```

**Figure 4.3** illustrates [description of what the figure shows]. [Brief description of visual patterns].

**Post-hoc Analysis** (if applicable):
- **Multiple comparisons**: [Results of post-hoc tests]
- **Pairwise comparisons**: [Specific comparisons and results]

## Research Question 2: [Question Text]

### Hypothesis 2: [Hypothesis Statement]

#### Primary Analysis

```{r}
#| label: tbl-rq2-primary
#| tbl-cap: "Primary Analysis Results for Research Question 2"

# Analysis results table will be generated here
```

**Primary Statistical Test**: [Test name]
- **Test statistic**: [statistic] = [value]
- **Degrees of freedom**: [df]
- **p-value**: p = [value]
- **Effect size**: [effect size measure] = [value]
- **Confidence interval**: [CI range]

**Result**: [Brief statement of statistical significance and direction]

#### Model Fit (if applicable)

```{r}
#| label: tbl-model-fit
#| tbl-cap: "Model Fit Statistics"

# Model fit indices will be generated here
```

**Table 4.5** presents model fit statistics:
- **Chi-square**: χ²([df]) = [value], p = [p-value]
- **CFI**: [value]
- **TLI**: [value]
- **RMSEA**: [value] (90% CI: [lower, upper])
- **SRMR**: [value]

## Research Question 3: [Question Text]

### Hypothesis 3: [Hypothesis Statement]

#### Primary Analysis

```{r}
#| label: tbl-rq3-primary
#| tbl-cap: "Primary Analysis Results for Research Question 3"

# Analysis results table will be generated here
```

**Primary Statistical Test**: [Test name]
- **Test statistic**: [statistic] = [value]
- **Degrees of freedom**: [df]
- **p-value**: p = [value]
- **Effect size**: [effect size measure] = [value]
- **Confidence interval**: [CI range]

**Result**: [Brief statement of statistical significance and direction]

#### Mediation/Moderation Analysis (if applicable)

```{r}
#| label: fig-mediation
#| fig-cap: "Path Model for Mediation Analysis"

# Path diagram will be generated here
```

**Figure 4.4** shows the path model for the mediation analysis. 

**Mediation Results**:
- **Direct effect**: b = [value], SE = [value], p = [p-value]
- **Indirect effect**: b = [value], SE = [value], 95% CI = [lower, upper]
- **Total effect**: b = [value], SE = [value], p = [p-value]

## Additional Analyses

### Exploratory Analysis

#### Unexpected Findings

[Description of any unexpected or interesting findings that emerged during analysis]

```{r}
#| label: fig-exploratory
#| fig-cap: "Exploratory Analysis Results"

# Additional visualizations will be generated here
```

#### Sensitivity Analysis

- **Outlier analysis**: [Results of outlier detection and impact]
- **Robustness checks**: [Results of alternative analytical approaches]
- **Missing data sensitivity**: [Results of different missing data handling approaches]

### Subgroup Analysis

#### Analysis by [Grouping Variable]

```{r}
#| label: tbl-subgroup
#| tbl-cap: "Subgroup Analysis Results"

# Subgroup analysis table will be generated here
```

**Table 4.7** presents results stratified by [grouping variable]:
- **Group 1**: [Results summary]
- **Group 2**: [Results summary]
- **Group comparison**: [Statistical test results]

## Qualitative Results (if applicable)

### Thematic Analysis

#### Theme 1: [Theme Name]

[Description of theme with supporting quotes]

> "Representative quote from participant" (Participant ID)

**Sub-themes**:
- **Sub-theme 1.1**: [Description]
- **Sub-theme 1.2**: [Description]

#### Theme 2: [Theme Name]

[Description of theme with supporting quotes]

> "Representative quote from participant" (Participant ID)

#### Theme Integration

```{r}
#| label: fig-thematic-map
#| fig-cap: "Thematic Map of Qualitative Results"

# Thematic map visualization will be generated here
```

**Figure 4.5** illustrates the relationships between identified themes.

## Summary of Results

### Key Findings

1. **Research Question 1**: [Brief summary of findings and statistical significance]
2. **Research Question 2**: [Brief summary of findings and statistical significance]
3. **Research Question 3**: [Brief summary of findings and statistical significance]

### Hypothesis Testing Summary

```{r}
#| label: tbl-hypothesis-summary
#| tbl-cap: "Summary of Hypothesis Testing Results"

# Summary table of all hypotheses will be generated here
```

**Table 4.8** summarizes the results of all hypothesis tests:
- **Hypothesis 1**: [Supported/Not supported] (p = [value])
- **Hypothesis 2**: [Supported/Not supported] (p = [value])
- **Hypothesis 3**: [Supported/Not supported] (p = [value])

### Effect Sizes

All reported effect sizes follow Cohen's conventions:
- **Small effects**: [effect size measure] ≈ [threshold]
- **Medium effects**: [effect size measure] ≈ [threshold]
- **Large effects**: [effect size measure] ≈ [threshold]

The current study found [summary of effect sizes and their practical significance].

## Chapter Summary

This chapter presented the results of the data analysis addressing the three research questions. The findings indicate that [brief summary of main findings]. [Summary of supported/unsupported hypotheses]. These results provide the foundation for the discussion and interpretation presented in the following chapter.